---
title: "JHUShiny Presentation"
author: "cybersuno"
date: "20/2/2021"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```



## Purpose

The objective of this presentation is to show the shiny application developed as part of the Johns Hopkins University week 4 for the _Developing Data Products_ course.

The purpose of the application is to show the linear regression between the different variables in the mtcars dataset. For this, two variables are selected and a linear model (lm) is fitted.
The application shows the coefficients for the linear model and a plot with the two variables and the correlation.

The _mtcars_ dataset has the following structure
```{r dataset}
str(mtcars)
```

## Application Input
The application requires two variables:

* Y var: this is the variable to be in the Y axis, and the variable to be estimated
* X var: this is the variable to be in the X axis, and the predictor in the model

The model is fitted with the following formula:
Y ~ X

We can build an example for the variables:

* Y = mpg
* X = disp

```{r model_fitted, echo=TRUE}
fit<-lm(mpg ~ disp,data=mtcars)

``` 

## Application Output: coefficients
The output is divided in two elements: coefficients for the model and plot with the regression

The coefficients are:

* Intercept
* Slope for the predictor

Each line have four entries. The information is the same as when the model is summarized:

* The value
* The standard error
* T value
* p-value

In our example, information showed could be:
```{r coefficients}
summary(fit)$coefficients
```

## Application Output: plot

A single plot is showed in which we can find:

* The points with the values for both of the variables in each axis
* The regression line calculated for the model

In our example:

```{r plot}
plot(mpg ~ disp,xlab="disp",ylab="mpg",data=mtcars)
abline(fit)
```


## Application Structure and link

Application is structured in a sidebar with the two combos to select the variables.


Anytime a variable is selected, reactively a new model is fitted and new output is calculated

If the same variable is selected for Y and X axis, no coefficients are calculated


The web can be accessed through the following link:
[Application](http://www.google.es)

The github repository link for the application (and this presentation) is the following:
[GitHub Link](https://github.com/cybersuno/JHUShiny)

